\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF at $t=0$ as
\begin{align*}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\end{align*}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter

@@

@@

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

>>>>

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF at $t=0$ as
\begin{align*}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\end{align*}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

@@

% === Power system book

\bibitem{andersonBook1977}
P.M.~Anderson, and A.A.~Fouad, \emph{Power System Control and Stability}, Iowa State University Press, Ames, IA, 1977.

\bibitem{kundurBook1994}
P.~Kundur, \emph{Power System Stability and Control}, McGraw-Hill, New York, 1994.

@@

%\begin{IEEEbiography}{Michael Shell}
%Biography text here.
%\end{IEEEbiography}
